### 2014-01-29 rscripts/manuscript.Rnw
updating manuscript

\section*{A Language Matching the Simulation Requirements: Scala}
Scala\cite{odersky2004overview} is an mixin-inheritance\cite{bracha1990mixin}, object-oriented, functional language, which also includes an message-passing based model for parallel computing\footnote{The actor model is transitioning from the initial implementation to that developed by the Akka project\cite{akka}.  We base our discussion on the Akka model.  The most important difference is the notion of contexts and context switching: with context switching, an actor alters how it responds to events.  This is a useful abstraction for representing evolving individual state.}.  Indeed, Scala is used under the hood for the network simulation framework NetLogo.

>>>>

\section*{A Language Matching the Simulation Requirements: Scala}
Scala\cite{odersky2004overview} is an mixin-inheritance\cite{bracha1990mixin}, object-oriented, functional language, which also includes an message-passing based model for parallel computing\footnote{The actor model is transitioning from the initial implementation to that developed by the Akka project\cite{akka}.  We base our discussion on the Akka model.  The most important difference is the notion of contexts and their switching and stacking: with a switching and stacking, an actor alters how it responds to events.  This is a useful abstraction for representing evolving individual state.}.  Indeed, Scala is used under the hood for the network simulation framework NetLogo.
